Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-29 second-draft/pnas-word-order-si.tex
SI

\paragraph{Grammar Example}

\begin{tabular}{llllllllll}
	                             & \multicolumn{3}{English}    &   \\
	Relation                     &     & $a_\tau$ & $b_\tau$   &   \\
	object (\textit{obj})        &     &          &            &   \\
	oblique (\textit{obl})       &     &          &            &   \\
	case (\textit{lifted\_case}) &     &          &            &   \\
\end{tabular}

@@

>>>>

\begin{figure}
	\begin{center}
\begin{tabular}{l||l|ll||l|lllll}
	& \multicolumn{3}{c||}{English}    &  \multicolumn{3}{c}{Japanese}  \\ 
	Relation                     &  Par.   & $a_\tau$ & $b_\tau$            & Par.   & $a_\tau$ & $b_\tau$     \\ \hline \hline
	object (\textit{obj})        &  $0.1$   &   $0.04$   & $-1.46$            & $-0.1$  & $0.99$ & $-0.7$2 \\
	oblique (\textit{obl})       &  $0.3$   &   $0.13$     & $1.25$             & $-0.3$  & $0.99$ & $0.73$ \\
	case (\textit{lifted\_case}) &  $0.2$   &   $0.07$       &   $-0.89$         & $-0.2$  &  $0.92$ & $0.02$  \\
\end{tabular}
	\end{center}
	\caption{Sample Coefficients from grammars extracted from the real English and Japanese orderings, for the relations occurring in Figure 3 (Main Paper). We show parameters in $[-1,1]$ for deterministic word order grammars, and the coefficients ($a_\tau, b_\tau$) for corresponding differentiable ordering grammars. For the deterministic grammars (`Par.'), positive coefficients indicate that the dependent will be placed after the head. For the differentiable grammars, $a_\tau > 0.5$ indicates ordering of dependents before heads, and larger $b_\tau$ indicates greater distance between head and dependent.}\label{fig:grammar-sample}
\end{figure}

@@

We provide an example in Figure~\ref{fig:grammar-sample}, illustrating grammar parameters for the relations in Figure 3 of the main paper.
